---
title: "Software Development Documentation for Iskay"
author: "Omar Benites"
date: "January 3, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file attemps to make an internal documentation for iskay nonparametric data analysis application. It includes:

1. Input and output object names

2. Import data

3. Dialogs event buttons

4. Combobox options buttons

5. Tables

6. Example for friedman test

## Input and output object names

- `uin_name`: widgets' name that run in the UI
- `ou_name`: widgets' name, for renderUI especifically, that use in the server
- `sel_name`: widget's name for selectInput in the server. It goes inside renderUI
- `ou_dtname`: widget's name for data tables running in the server.

## Import data

- `uin_fb_import`: widgets' name for fileInput. Upload data event for posterior d.analysis.
- `ou_sheets`: widget renderer that run in the server.
- `show_dlgImport`: widget for importing file dialog.


## Show dialogs
- `show_dlg(Name)`: dialog windows for displaying information about input's test

## ComboBox for statistical tables

- `cbTable_abbre_test`. combobox for statistical table as a result of applying different test.
  
This list includes thre main columns:  
```{r,warning=FALSE, echo=FALSE, message=FALSE, cache =FALSE}
  library(knitr)
  library(kableExtra)
  library(dplyr)
  Name <- c("Global summary", "Multiple comparison", "Paired comparison") 
  Choice <- c("gsum", "mulcom", "pcom") 
  pt <- data.frame(Name, Choice)
  kable(pt) 
```


## Import data 

- `show_dlgImport`. 

Type: **Action button**. 
Description: show help dialog about the test and required inputs

## Tables for test results

There are three types of tables:

 * `ou_dt(test_abvreviation)_gsum` 
 
Type: **DataTable**.
 
Description: descriptive summary. Ex: ``ou_dtmanw_gsum`` (Mann-Withney summary descriptive).
 
* `ou_dt(test_abbreviation)`
 
Type: **DataTable**.
  
Description: p-values, mean or median multiple comparison. Ex. ``ou_dtmanw`` (Mann-Whitney analysis results/table), 
 
 - `out_dt(test_abbreviation)_pair`
 
Type: **DataTable**.
   
Description: paired comparison. Ex. ``ou_dtfriedman_pair`` (Friedman test paired   comparison table).

## Test results

- `test_result`: 
  Type: **Reactive data**

  Description: Reactive data. Storage the results for each test using the tabName (tab name for each test).

## Friedman Test: Inputs and outputs

### Friedman renderUI 

- `uiOutput("ou_resfrman")`
- `uiOutput("ou_trtfrman")`
- `uiOutput("ou_blocksfrman")`

### Friedman selectInput

- `sel_input_resfrman`
- `sel_input_resfrman`
- `sel_input_resfrman`

### Friedman data table

- `ou_dtfrman`

### Friedman show dialog

- `show_dlgFriedman`




# TODO: #parameter table
        #statistic table
        #radial plot



# References

* http://www.kovcomp.co.uk/xlstat/tools/non-parametric-tests-on-k-independent-samples.html
* http://bolt.mph.ufl.edu/files/2013/03/image094.gif
* http://www.sthda.com/english/wiki/paired-samples-wilcoxon-test-in-r
